QuantCoin\texttrademark\,-- A quantum computation-backed cryptocurrency

### 2018-08-15 Junk/QuantCoin/quantcoin.tex

%
% Economics & Politics of the Quantum Internet
%

\dropcap{A}{ny} form of computation comes at an economic cost, but also brings with it a payoff. A key consideration in any model for computation is the tradeoff between the two. Because the computational power of quantum computers scales inherently differently than classical computers, we expect economic indicators to exhibit different scaling characteristics and dynamics also, thereby fundamentally altering the economic landscape of the post-quantum world.

We will now treat some of these economic issues in the context of a global network of unified quantum computing resources, which are then equitably time-shared\index{Time-sharing}. We argue in Sec.~\ref{sec:time_share} that this time-shared model for quantum computation is always more computationally efficient than having distinct quantum computers operating independently in parallel, owing to the super-linear scaling in their joint computational power. While this section provides mathematical details of various economic models, Secs.~\ref{sec:economics} \& \ref{sec:quant_coin_essay} provide a popular, high-level discussion surrounding these issues.

%
% Classical-Equivalent Computational Power & Computational Scaling Functions
%

\section{Classical-equivalent computational power \& computational scaling functions}\index{Classical-equivalent computational power}\index{Computational scaling functions}\label{sec:comp_sc_func}

\dropcap{L}{et} $t$ be the classical-equivalent runtime\index{Classical-equivalent computational power} of a quantum algorithm comprising $n$ qubits -- that is, how long would a given classical computer require to implement this $n$-qubit quantum computation? We define a \textit{computational scaling function}\index{Computational scaling functions} characterising this relationship,

\begin{definition}[Computational scaling functions] \label{def:scaling_func}\index{Computational scaling functions} 
The computational scaling function, $f_\mathrm{sc}$, relates the number of qubits held by a quantum computer, $n$, and the classical-equivalent runtime, $t$, of the algorithm it implements,
\begin{align}
t = f_\mathrm{sc}(n),
\end{align}
	where $f_\mathrm{sc}$ is monotonically increasing, and depends heavily on both the algorithm being implemented, as well as the architecture of the computer.
\end{definition}

The exact form of the scaling function will be specific to the algorithm being deployed\footnote{For example, the \textit{circuit depth}\index{Circuit depth}, i.e number of gate applications in series, will heavily influence the number of classical steps required to simulate the circuit.}, and the computational model (e.g cluster states vs the circuit model, as well as choices in error correction, amongst other factors). Most notably, different quantum algorithms offer different scalings in their quantum speedup -- Grover's algorithm (Sec.~\ref{sec:quantum_search})\index{Grover's algorithm} offers only a quadratic quantum speedup, compared to the exponential speedup afforded by Shor's algorithm (Sec.~\ref{sec:shors_alg})\index{Shor's algorithm}. Thus, the computational scaling function depends on both the hardware and software, and may therefore differ between different users operating the same computer.

%
% Virtual Scaling Functions
%

\subsection{Virtual computational scaling functions}\index{Virtual computational scaling functions}

If a network of quantum computers were combined into a single, larger \textit{virtual quantum computer}\index{Virtual quantum computer} (Sec.~\ref{sec:GVQC}) using a distributed model for quantum computation (Sec.~\ref{sec:dist_QC}), we can define a computational scaling function relationship for the virtual device,

\begin{definition}[Virtual scaling function]\index{Virtual computational scaling functions}
The joint classical-equivalent runtime of a distributed virtual quantum computation over a network is,
\begin{align}
t_\mathrm{joint} = f_\mathrm{sc}^\mathrm{virtual}(n_\mathrm{global}),
\end{align}
where,
\begin{align}
n_\mathrm{global} = \sum_{j\in\mathrm{nodes}} n_j,
\end{align}
is the total number of qubits in the network, with $j$ summing over all nodes in the network, each of which holds $n_j$ qubits. $f_\mathrm{sc}^\mathrm{virtual}$ is obtained from $f_\mathrm{sc}$ by factoring in network overheads and inefficiencies. With perfect network efficiency, \mbox{$f_\mathrm{sc}^\mathrm{virtual}=f_\mathrm{sc}$}.
\end{definition}

%
% Combined Computational Scaling Functions
%

\subsection{Combined computational scaling functions}\index{Combined computational scaling functions}\label{sec:comb_comp_sc_func}

Until now we have characterised the entire network by a single scaling function. Of course, the scaling functions observed by different market participants needn't all be the same, as they are functions of not only the hardware, but also the participants' different algorithmic applications (i.e software).

Consider taking a single unit of time (i.e we are ignoring cost discounting\index{Cost discounting} over multiple units of time) and dividing it amongst a number of nodes, $n_\mathrm{nodes}$, each with their own scaling function, $f_\mathrm{sc}^{(i)}$. The total classical-equivalent runtime of the computation is additive, given simply by a linear combination of the classical-equivalent processing times of the individual nodes. This yields the relationship for combining scaling functions,
\begin{definition}[Combined scaling functions]\index{Combined computational scaling functions}\label{def:comb_sc_func}
The effective combined computational scaling function, $f_\mathrm{sc}^\mathrm{(joint)}$, of a group of participants, each with their own scaling functions, $f_\mathrm{sc}^{(i)}$, is given by,
\begin{align}
	t_\mathrm{joint} &= \sum_{i=1}^{n_{\mathrm{nodes}}} \beta_i \cdot f_\mathrm{sc}^{(i)}(n_\mathrm{global}) \nonumber \\
	&= f_\mathrm{sc}^\mathrm{(joint)}(n_\mathrm{global}),
\end{align}
where $\beta_i$ characterise the share of processing time allocated to each node, and for normalisation,
\begin{align}
\sum_{i=1}^{n_\mathrm{nodes}} \beta_i = 1.
\end{align}

\end{definition}

Thus, the joint scaling function of the entire network is simply given by a linear combination (weighted average) of the scaling functions of the different market participants.

%
% Network Price Scaling Factor
%

\section{Network price scaling factor}\label{sec:NPSF}\index{Network price scaling factor}

\dropcap{O}{ne} parameter that appears ubiquitously in the upcoming economic models and warrants a definition of its own is the computational power of a quantum computer per qubit. This relates the power and size of the computer. We define this as the \textit{network price scaling factor},

\begin{definition}[Network price scaling factor]\label{def:NPSF}\index{Network price scaling factor}
The network price scaling factor is defined as the computational power per qubit,
\begin{align}
\chi_\mathrm{sc}(n) = \frac{f_\mathrm{sc}(n)}{n}.
\end{align}
\end{definition}

This parameter acts as an overall, network size-dependent price scaling factor on:
\begin{itemize}
\item Quantum computational leverage (Sec.~\ref{sec:quant_ec_lev}).
\item Cost of computation (Sec.~\ref{sec:cost_of_comp}).
\item Time-shared computational power (Sec.~\ref{sec:arb_free_time_share}).
\item Quantum computational leverage (Sec.~\ref{sec:quant_ec_lev}).
\item Forward contracts (Sec.~\ref{sec:for_contr}).
\end{itemize}

This lends itself to the elegant interpretation as a cost multiplier on qubit asset, dividend and derivative prices, which warrants investigation of its scaling characteristics, shown in Fig.~\ref{fig:NPSF}. The key observation is that this scaling factor is constant for classical computing, where the scaling function is linear, but monotonically increasing for any super-linear scaling function. For polynomial scaling functions, it has the effect of reducing the order of the polynomial by one. And for exponential scaling functions, it remains exponential.

\begin{figure}[htb!]\index{Network price scaling factor}
	\includegraphics[width=0.47\textwidth]{network_price_scaling_factor}
	\caption{Network price scaling factor, $\chi_\mathrm{sc}$, as a function of several representative computational scaling functions, $f_\mathrm{sc}$, where $n$ is network size.} \label{fig:NPSF}
\end{figure}

%
% Time-Sharing
%

\section{Time-sharing}\label{sec:time_share}\index{Time-sharing}

\dropcap{S}{uppose} Alice and Bob both possessed expensive classical Cray\texttrademark\,supercomputers\index{Supercomputers}, both identical. They're both connected to the internet, so does it make sense to unify their computational resources over the network to construct a more powerful virtual machine\index{Virtual quantum computer}, which they subsequently time-share\index{Time-sharing} between themselves, or are they better off just using their own computers independently?

If there were an asymmetry in demand for computational resources, it would make perfect sense to unify computational resources, so as to mitigate wasting precious clock-cycles. However, if they were both heavy users, always consuming every last clock-cycle, it would make no difference: for a given computation, Alice and Bob could each be allocated half the processing time of the virtual supercomputer twice as powerful; or, each could exploit the full processing time of their half-as-fast computers. In either case, the dollar cost of the computation is the same. This simple observation follows trivially from the linear relationship between processing power and the number of CPUs in a classical computer.

More generally, in a networked environment where time-sharing\index{Time-sharing} of classical computational resources is applied equitably, proportionate to nodes' contribution to the network, the dollar cost per computation is (roughly, modulo parallelisation overheads) unaffected by the rest of the network. Instead, the motivation for networking computational resources is to improve efficiency by ensuring that clock-cycles are not wasted, but instead distributed according to demand by a scheduling algorithm, which could be market-driven, for example.

However, the computational power of a quantum computer generally doesn't scale linearly with its number of qubits, but super-linearly, often exponentially. This completely changes the economics, and market dynamics of networked quantum computers. Intuitively, we expect equitable time-sharing of unified quantum computational resources to offer more performance to all nodes than if they were to exclusively use their own resources in isolation. That is, the cost of a computation is reduced by resource-sharing, even after time-sharing.

For this reason, henceforth we will assume an environment in which owners of quantum hardware network and unify their computational power, sharing the virtual quantum computer's power between them.

In Sec.~\ref{sec:arb_free_time_share} we present an explicit model for equitable time-sharing, which is optimal from a market perspective.

%
% Economic Model Assumptions
%

\section{Economic model assumptions}

\dropcap{B}{efore} proceeding with explicit derivations of economic models, we state some assumptions about the dynamics of a marketplace in quantum assets. These assumptions are largely based on historical observations surrounding classical technologies that we might reasonably expect to also apply in the quantum era. However, given that the quantum marketplace is one that hasn't been explored in detail until now, it may be the case that some of these assumptions will require revision. Nonetheless, the general techniques we employ could readily be adapted to some relaxations and variations in these assumptions.

%
% Efficient Markets
%

\subsection{Efficient markets}\label{sec:eff_markets} \index{Efficient markets}

We make several assumptions about the efficiency of the quantum marketplace. These are largely based on the conventional efficient-market hypothesis (EMH)\index{Efficient-market hypothesis (EMH)} \cite{???}, readily taught in undergraduate ECON101 and subsequently summarily rejected upon entering ECON202. For ease of exposition, we will remain in the ECON101 classroom.

Some of these assumptions may reasonably turn out to be invalid, or require revision as we learn more about upcoming quantum technologies and the trajectories their marketplace will follow. However, for ease of exposition, and the purposes of presenting some initial rudimentary, \textit{qualitative} analyses and thought experiments, these assumptions simplify our derivations and act as a good starting point for future, more rigorous treatment (which we highly encourage!).

Given that the quantum marketplace doesn't actually exist yet, it isn't immediately clear which assumptions are likely to be valid or not, and future, more sophisticated models will inevitably need to make more appropriate assumptions. Certainly it's no secret that in conventional settings the EMH is flawed in many respects, and some of its idealised assumptions break down in reality.

\begin{postulate}[Efficient markets]\label{post:market_eff}\index{Efficient markets} We make the following efficiency assumptions on the dynamics of the quantum marketplace:
\begin{itemize}
	\item Qubits are a `scarce' resource --- there is always positive, non-zero demand for them.\index{Scarce resource}
	\item No wastage --- quantum computational resources are always fully utilised, with no down-time.\index{Wastage}
	\item Transaction free --- transaction costs are negligible, for both quantum assets and their derivatives.\index{Transaction cost}
	\item Negligible cost-of-carry --- e.g storage and maintenance costs are negligible.\index{Cost of carry}
	\item High liquidity --- it is always possible to execute transactions at market rates.\index{Liquidity}
	\item Perfect competition --- there are no monopolies gouging prices, which are in equilibrium.\index{Perfect competition}
	\item Arbitrage-free --- market rates for different assets and derivatives are perfectly consistent, with no opportunity for `free money' by trading on market discrepancies.\index{Arbitrage-free}
	\item Perfect information --- all market participants have complete knowledge of all market variables, including one another.\index{Perfect information}
	\item Rational markets --- all market participants act rationally\footnote{i.e with perfect economic self-interest \latinquote{Avaritia}.} upon available information.\index{Rational markets}
	\item Indefinite asset lifetime --- there is no deterioration or death of quantum hardware over time.\index{Asset lifetime}
	\item There is a risk-free rate of return ($r_\mathrm{rf}$)\index{Risk-free rate of return}
-- the rate of growth exhibited by an investment into an optimal risk-free asset\footnote{Historically these risk-free assets are taken as being US government bonds\index{US government bonds}\index{Risk-free asset}, with the bond yield being the risk-free RoR.}
	\end{itemize}
\end{postulate}

%
% Central Mediating Authority
%

\subsection{Central mediating authority}\index{Central mediating authority}

In Sec.~\ref{sec:time_share} we argued that because of the super-linear scaling in the computational power of networked quantum computers, it will be most economically efficient to unify the world's entire collective quantum computational resources over the network and time-share their joint computational power. For this reason, we will assume that global quantum computing resources are unified, and time-shared equitably (as will be described in Sec.~\ref{sec:arb_free_time_share}), overseen by a trusted central authority, congruent with our efficient market assumptions (Sec.~\ref{sec:eff_markets}).

The role of the mediating authority is to perform process scheduling\index{Scheduling} -- equitably allocating algorithmic runtime on the virtual computer to the different network participants. This could be in the form of a state-backed authority, or open market-driven alliances. In any case, the job of the authority is a relatively straightforward one, and we will assume it induces negligible cost and computational overhead, remaining largely transparent to the end-user.

However, as discussed in Sec.~\ref{sec:GVQC}, it may be the case that competing strategic interests will drive a wedge between the quantum resources of competitors and adversaries, partitioning them into a set of smaller networks, divided across strategic boundaries. In this instance, the arguments presented in the upcoming sections will apply to these smaller, isolated networks individually.

%
% Network Growth
%

\subsection{Network growth} \index{Network growth}

We assume the number of qubits in the global network in the future is growing exponentially over time, i.e the rate of progress of quantum technology will observe a Moore's Law-like behaviour, as with the classical transistor.

This is a reasonable assumption based on the observation of this ubiquitous kind of behaviour in present-day technologies. Classical computing has been on an exponential trajectory since the 1980's, and although it must eventually asymptote, it shows no sign of doing so in the immediate future. Quantum technologies sit at the entry point to this trajectory, and we expect it to continue for the medium-term. Thus, we let the number of qubits in the network be,
\begin{postulate}[Network growth]\label{post:net_growth}\index{Network growth postulate}
The number of qubits in the global quantum internet is growing exponentially over time as,
\begin{align}
	N(t) = N_0 {\gamma_N}^{t},
\end{align}
where \mbox{$\gamma_N\geq 1$} characterises the rate of exponential growth in the number of qubits available to the quantum network.
\end{postulate}

The exact value of the growth rate, $\gamma_N$, is obviously unclear at such early stages and will ultimately be determined empirically. Although in the the case of classical computing we have seen a very consistent doubling of computational power roughly every 18 months. This may very well be different for quantum technologies, owing to their fundamentally different engineering requirements (which are far more challenging in general).

%
% Hardware Cost
%

\subsection{Hardware cost} \index{Hardware cost}

Let the dollar cost of physical qubits follow Moore's Law-like dynamics, decreasing exponentially with time,
\begin{postulate}[Hardware cost]\label{post:hardware_cost}\index{Hardware cost}
The dollar-cost of a single physical qubit scales inverse exponentially against time as,
\begin{align}
	C(t) = C_0 {\gamma_C}^{-t},
\end{align}
where \mbox{$\gamma_C\geq 1$} characterises the decay rate.
\end{postulate}

This is consistent with the observed evolution of classical hardware since the beginning of the digital revolution, and it is reasonable to think that technological progress in the quantum era will follow a similar trajectory.

%
% Network Power
%

\section{Network power}\index{Network power}\label{sec:network_power}

\dropcap{F}{irst} and foremost, with a fully interconnected quantum computational network, what is the projection of its net computational power now and into the future? This is simply obtained via the joint computational scaling function applied to projected network size,

\begin{postulate}[Network power]\label{post:network_power}\index{Network power}
The combined computational power of the entire network, measured in classical-equivalent runtime (i.e FLOPs), is given by,
\begin{align}
P(t) &= f_\mathrm{sc}(n_\mathrm{global})\nonumber \\
&= f_\mathrm{sc}(N_0{\gamma_N}^t).
\end{align}
\end{postulate}

%
% Network Value
%

\section{Network value}\index{Network value}\label{sec:network_value}

\dropcap{T}{he} simplest economic metric one might define is the collective dollar value of the entire network. That is, the product of the number of qubits on the network and the dollar cost per physical qubit at a given time.

\begin{postulate}[Network value]\label{post:network_value}\index{Network value}
The dollar-value of the entire network is given by,
\begin{align}
	V(t) &= C(t) N(t) \nonumber \\
	&= C_0 N_0 \left(\frac{\gamma_N}{\gamma_C}\right)^t.
\end{align}
\end{postulate}

Note that the collective value of the network appreciates exponentially if the rate of network growth is greater than the rate of decay in the value of physical qubits, otherwise it depreciates. At \mbox{$\gamma_C=\gamma_N$} the network's dollar value remains constant over time. This is shown in Fig.~\ref{fig:network_value}.

\begin{figure}[htpb]
	\includegraphics[width=0.4\textwidth]{network_value}
	\caption{Dollar value (in units of \mbox{$C_0N_0$}) of the network as a function of time, growth rate in the number of physical qubits, and rate of decay in the dollar value of physical qubits. When \mbox{$\gamma_N/\gamma_C=1$} the network's value remains constant over time. Above this the network's value appreciates exponentially, and below which it depreciates exponentially against time.} \label{fig:network_value}
\end{figure}

%
% Rate of Return
%

\section{Rate of return}\index{Rate of return}

\dropcap{T}{he} execution of computations typically has monetary value to the consumer. After all, they are paying hard-earned money for access to the technology!

Suppose the owners of the quantum hardware are not running computations themselves, but rather are collectively licensing out their joint compute-time to end-users. The hardware owners will of course be demanding a profit from their enterprise. The rate at which they earn back their investment into hardware via the licensing of compute-time, we will refer to as the rate of return (RoR), $\gamma_\mathrm{ror}$. We define this as,

\begin{postulate}[Rate of return]\label{post:RoR}\index{Rate of return}
The RoR is defined as,
\begin{align}
e^{\gamma_\mathrm{ror}} = \frac{n_\mathrm{return}}{n_\mathrm{cost}},
\end{align}
where $n_\mathrm{return}$ is the profit made by licensing out the network's joint compute-power for a single unit of time, given a present-day network value of $n_\mathrm{cost}$.
\end{postulate}

A higher $\gamma_\mathrm{ror}$ implies a faster payback rate on hardware investment\footnote{We have parameterised the RoR as an exponential for convenience when performing derivations with compounding.}.

In an ideal market, where hardware cost is completely predictable, e.g perfectly follows the hardware cost model (Pos.~\ref{post:hardware_cost}), the risk asymptotes to zero and perfect arbitrage (Pos.~\ref{post:market_eff}) will drive the RoR to asymptote to the risk-free RoR, \mbox{$\gamma_\mathrm{ror} \to r_\mathrm{rf}$}. Of course, real markets necessarily exhibit risks and uncertainties, and the RoR on quantum hardware will never be truly risk-free, meaning that upon trading off risk for return, we will always observe \mbox{$\gamma_\mathrm{ror} > r_\mathrm{rf}$}.

%
% Cost Of Computation
%

\section{Cost of computation}\label{sec:cost_of_comp} \index{Cost of computation}

\dropcap{I}{n} the same scenario as before, where compute-time is being licensed out to end-users, the hardware owners return over a single unit of time equates to the cost of computation over that period.

Let $L(t)$ be the dollar-value of utilising the network's computing resources for a single unit of time. This is obtained as the return made on the value of the network per FLOP,
\begin{postulate}[Cost of computation]\label{post:cost_comp}
The efficient-market dollar-value of a computation for a single unit of time at time $t$, per FLOP is,
\begin{align}\index{Cost of computation postulate}
	L(t) &= \frac{e^{\gamma_\mathrm{ror}} P(t)}{V(t)} \nonumber\\
	&= \frac{e^{\gamma_\mathrm{ror}} C_0{\gamma_C}^{-t}}{\chi_\mathrm{sc}(N_0 {\gamma_N}^t)},
\end{align}
\end{postulate}
which implies,
\begin{postulate}[Spot price of computation]\index{Spot price of computation} The present-day (\mbox{$t=0$}) spot price of a computation per FLOP is,
\begin{align}
L(0) = \frac{e^{\gamma_\mathrm{ror}}C_0}{\chi_\mathrm{sc}(N_0)}.	
\end{align}
\end{postulate}
That is, the value of computations simply approximates the return on initial hardware investment, scaled by its initial computational power, as is intuitively expected.

Note that if $f_\mathrm{sc}$ scales linearly, as per classical computation, we observe a regular exponential decay in the cost of computation, consistent with the classical Moore's Law. On the opposing extreme, for exponentially quantum-enhanced $f_\mathrm{sc}$, the cost of computation decreases super-exponentially with time, an economic behaviour unique to post-classical computation with no classical analogue.

The time-derivative of the cost of computation is strictly negative, assuming correctness of the growth and cost postulates (Pos.~\ref{post:net_growth} \& \ref{post:cost_comp}),
\begin{align}
\frac{\partial L}{\partial t} \leq 0,	
\end{align}
which implies monotonic reduction in the cost of computation over time, unless network growth and cost completely freeze (\mbox{$\gamma_N=\gamma_C=0$}), in which case the cost of computation remains flat.

Examples of the temporal dynamics of the cost of computation are shown in Fig.~\ref{fig:econ_cost_of_comp} for representative computational scaling functions.

\begin{figure*}[htpb]
\includegraphics[width=0.325\textwidth]{cost_of_comp_n}
\includegraphics[width=0.325\textwidth]{cost_of_comp_n2}
\includegraphics[width=0.325\textwidth]{cost_of_comp_2n}
\caption{Examples of the temporal dynamics of the cost of computation for different scaling functions and exponential growth rates. Units are \mbox{$C_0=N_0=n=1$}, with RoR \mbox{$\gamma_\mathrm{ror}=0$}. A non-zero RoR would simply scale these figures by a constant factor of $e^{\gamma_\mathrm{ror}}$.}\label{fig:econ_cost_of_comp}
\end{figure*}

%
% Arbitrage-Free Time-Sharing
%

\section{Arbitrage-free time-sharing model}\label{sec:arb_free_time_share} \index{Arbitrage-free time-sharing model}\index{Time-sharing}

\dropcap{I}{n} the context of our time-shared global network of unified quantum computers (Sec.~\ref{sec:time_share}), how do we fairly and equitably allocate time-shares between contributors? We now derive an elementary arbitrage-free model for equitable time-sharing in such a network.

Let,
\begin{align}
	0\leq r_n \leq 1,
\end{align}
be the proportion of compute-time allocated to a node in possession of $n$ qubits, in a global network of $n_\mathrm{global}$ qubits. Arbitrage in the value of physical qubits will enforce the linearity constraint,
\begin{align}
	r_{n_1+n_2} = r_{n_1} + r_{n_2}.
\end{align}
This constraint effectively mandates that `all qubits are created equal', and two qubits are twice as valuable as one \latinquote{Qubit aequalitatem}. Were, for example, a bundle of two qubits more expensive than two individual qubits purchased in isolation, a market participant could perform arbitrage and unfairly gain free compute-time by buying two qubits separately, unifying them, selling the bundle, buying them back individually, and repeating indefinitely until he seizes the entire network.

Additionally, we have assumed no compute-cycles are wasted -- compute-time is always fully utilised, as per Pos.~\ref{post:market_eff}. Then it follows that the time-share of the combined resources of the entire network should be unity,
\begin{align}
	r_{n_\mathrm{global}}=1.
\end{align}
\mbox{$r_{n_\mathrm{global}}<1$} would imply inefficiency via wasted clock-cycles. Combining this with the linearity constraint implies the arbitrage-free time-sharing model,
\begin{definition}[Arbitrage-free time-sharing model] \label{def:arb_free_ts}\index{Arbitrage-free time-sharing model}
In an efficient market for unified quantum computing time-shares\index{Time-sharing}, a network participant in possession of $n$ of the entire $n_\mathrm{global}$ qubits in the network is entitled to the fraction of unified network compute time,
\begin{align}\index{Time-shared compute-time}
	r_n = \frac{n}{n_\mathrm{global}},
\end{align}
where,
\begin{align}
n_\mathrm{global} = \sum_{j\in\mathrm{nodes}} n_j,
\end{align}
is the total number of qubits in the network, and,
\begin{align}
0\leq r_n \leq 1.	
\end{align}
\mbox{$r_n=1$} iff the node has a complete monopoly over qubits, i.e \mbox{$n=n_\mathrm{global}$}.
\end{definition}

Based on this equitable model for time-sharing,
\begin{definition}[Time-shared computing power]\index{Time-shared computing power}
The computing power allocated to each user under the arbitrage-free time-sharing model is,
\begin{align}
	c_n &= r_n \cdot f_\mathrm{sc}(n_\mathrm{global}) \nonumber \\
	&= n \cdot \chi_\mathrm{sc}(n_\mathrm{global}).
\end{align}
\end{definition}

This model is intuitively unsurprising, since it is analogous to the case of classical computer clusters -- nodes receive a time-share proportional to the proportion of the hardware they are contributing to the network. However, it is important to point out that the arbitrage is taking place in the cost of physical qubits, but not in terms of the dollar value of their classical-equivalent processing power, since this is in general non-linearly related to the number of qubits. Arbitrage in computational power per se is complicated by the fact that it is a non-fungible asset that cannot be directly traded, or uniquely associated with a tangible, tradable asset -- its computational value is a function of other assets.

%
% Problem Size Scaling Functions
%

\section{Problem size scaling functions}\index{Problem size scaling functions}\label{sec:prob_sc_func}

\dropcap{T}{he} computational scaling function\index{Computational scaling functions} introduced previously expresses the power of a quantum computer in terms of its classical-equivalent runtime, or equivalently FLOPs\index{FLOPs}. However, this may not be the metric of interest when considering a computer's algorithmic power. In many situations, of far greater interest is the size of a problem\index{Problem size} instance that can be solved in a given timespan. For example, the FLOPs associated with solving an instance of a 3-\textsc{SAT} problem\index{3-SAT problem} grows exponentially with the number of clauses. When discussing the execution of this problem on a given computer, what we really want to know is how many clauses our device can cope with, rather than what the classical-equivalent runtime is.

This observation motivates us to re-parameterise the power of quantum computers in terms of the problem size of a given algorithm to be solved. Employing the same methodology as for computational scaling functions, we define the \textit{problem size scaling function}, which relates the size of an algorithmic problem to it's classical equivalent runtime. Then equating the computational and problem size scaling function yields,

\begin{definition}[Problem size scaling function]\index{Problem size scaling functions}
The problem size scaling function relates the size of a problem instance ($s$), in some arbitrary metric, to its classical-equivalent runtime ($t$) under a time-shared network model,
\begin{align}
t = f_\mathrm{size}(s).
\end{align}
Equating this with the time-shared computational power yields,
\begin{align}
	n\cdot \chi_\mathrm{sc}(n_\mathrm{global}) = f_\mathrm{size}(s).
\end{align}
Isolating the problem size yields,
\begin{align}
s = f_\mathrm{size}^{-1}(n\cdot \chi_\mathrm{sc}(n_\mathrm{global})).
\end{align}
\end{definition}

We now consider several choices of scaling functions.

First let us consider the classical case of linear scaling functions (for both the computational and problem size scaling functions),
\begin{align}
	f_\mathrm{sc}(n) &= \alpha_\mathrm{sc} n,\nonumber\\
	f_\mathrm{size}(s) &= \alpha_\mathrm{size} s.
\end{align}
Solving for the problem size simply yields,
\begin{align}
s &= \frac{n}{\alpha_\mathrm{size}} \nonumber\\
&= O(1),
\end{align}
where $n$ is regarded as a constant, and $n_\mathrm{global}$ is a variable parameter of the network. That is, the problem sizes of solvable instances is independent of the size of the external network with whom we are time-sharing. This is to be expected, since these scaling functions are typical of classical computers.

For polynomial scaling functions,
\begin{align}
f_\mathrm{sc}(n) &= n^{p_\mathrm{sc}},\nonumber\\
f_\mathrm{size}(s) &= s^{p_\mathrm{size}}.
\end{align}
This yields problem size,
\begin{align}
	s &= (n \cdot {n_\mathrm{global}}^{p_\mathrm{sc}-1})^\frac{1}{p_\mathrm{size}} \nonumber\\
	&= O(\mathrm{poly}(n_\mathrm{global})),
\end{align}
demonstrating polynomial scaling in our solvable problem size against the size of the network.

For exponential scaling functions,
\begin{align}
f_\mathrm{sc}(n) &= e^{\alpha_\mathrm{sc}n},\nonumber\\
f_\mathrm{size}(s) &= e^{\alpha_\mathrm{size}s},
\end{align}
we obtain,
\begin{align}
s &= \log\left(n \frac{e^{\alpha_\mathrm{sc}n_\mathrm{global}}}{\alpha_\mathrm{sc}n_\mathrm{global}}\right) \nonumber\\
&= \alpha_\mathrm{sc}n_\mathrm{global} + \log(n)-\log(\alpha_\mathrm{sc}n_\mathrm{global}) \nonumber\\
&= O(n_\mathrm{global}),
\end{align}
demonstrating that the solvable problem size grows linearly with network size. That is to say, waiting for a doubling in the external network's size will also double the size of a \textbf{BQP}-complete\index{BQP} problem that can be solved in the same time.

%
% Quantum Computational Leverage
%

\section{Quantum computational leverage}\label{sec:quant_ec_lev}\index{Quantum computational leverage}

\dropcap{I}{n} Secs.~\ref{sec:dist_QC} \& \ref{sec:module} we introduced distributed and modularised quantum computation. Using this as a toy model, we will now investigate the market dynamics of uniting the quantum computational resources of multiple market participants, as per an equitable time-sharing model (Sec.~\ref{sec:time_share}). We envisage a model whereby network participants are contributing modules to the networked quantum computer, thereby unifying their computational power.

The $i$th node is contributing the fraction of the hardware $r_i$, and receives this same proportion of compute-time under the arbitrage-free time-sharing model (Def.~\ref{def:arb_free_ts}). This discounts his classical-equivalent processing time\index{Classical-equivalent computational power} to,
\begin{align}
\tau_i = t_\mathrm{joint} \cdot r_i.
\end{align}

We are now interested in quantifying how much better off individual contributors are under this model than they were individually. Let us define the \textit{quantum computational leverage}\index{Quantum computational leverage} (QCL) of a node's quantum computer to be the ratio between their unified time-shared and individual classical-equivalent processing times\index{Classical-equivalent computational power},
\begin{align}
\lambda_i = \frac{\tau_i}{t_i},
\end{align}
yielding the QCL formula,

\begin{definition}[Quantum computational leverage] \label{def:quant_econ_lev}\index{Quantum computational leverage formula}\index{Single-qubit quantum computational leverage}
For the $i$th node, and with scaling function $f_{sc}$, the QCL is defined as the ratio between the unified time-shared and individual classical-equivalent algorithmic runtimes,
\begin{align}
\lambda_i &= \frac{\tau_i}{t_i} \nonumber \\
&= \frac{n_i}{n_\mathrm{global}} \cdot \frac{f_{sc}(n_\mathrm{global})}{f_{sc}(n_i)}, \nonumber \\
&= \frac{\chi_\mathrm{sc}(n_\mathrm{global})}{\chi_\mathrm{sc}(n_i)},\nonumber\\
\lambda_i^\mathrm{dB} &= 10\log_{10}(\lambda_i),
\end{align}
where,
\begin{align}
	n_\mathrm{global} = \sum_{j\in \mathrm{nodes}} n_j,
\end{align}
is the total number of qubits in the network. The logarithmic version of the representation in decibels is simply a convenience when dealing with exponential scaling functions.
\end{definition}

Effectively, the QCL tells us how much additional computational power we `get for free' by consolidating with the network.

It is extremely important to note that the QCL is asymmetric, in the sense that the leverage achieved by a given node is larger than the leverage achieved by the network, upon the user joining the network (assuming the remainder of the network comprises more qubits than the respective user).

More generally, smaller users achieve higher computational leverage from their investment into quantum hardware than larger users. Specifically,
\begin{align}
	\lambda_i<\lambda_j \,\,\mathrm{for}\,\,n_i>n_j.
\end{align}

For any super-linear scaling function we have \mbox{$\lambda_i > 1 \,\,\forall \, i$}, and for any linear scaling function we have \mbox{$\lambda_i = 1 \,\,\forall \, i$},
\begin{align}
	\lambda=1\,\,\forall\,\,f_\mathrm{sc}(n)=O(n), \nonumber \\
	\lambda>1\,\,\forall\,\,f_\mathrm{sc}(n)>O(n).	
\end{align}

For \mbox{$\lambda_i>1$} it is always computationally beneficial to all nodes to unify computational resources and time-share them equitably, as per the arbitrage-free time-sharing model. Similarly, the distributed network is better off accepting them into the network, albeit to a lesser extent for a large network.

This is in contrast to classical networks, where \mbox{$\lambda\approx 1$}, for any number of nodes in the network (i.e there is no leverage), and it makes no difference whether nodes unify resources or operate independently.

Finally, in the pathological case, where \mbox{$\lambda_i<1$}, nodes are better off working in isolation, a situation which would only naturally arise as a result of algorithmic inefficiencies in parallelisation or distribution.

>>>>

\documentclass[aps,pra,twocolumn,amsmath,amssymb,nofootinbib,superscriptaddress]{revtex4}

\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\op}[2]{\hat{\textbf{#1}}_{#2}}
\newcommand{\dagop}[2]{\hat{\textbf{#1}}_{#2}^\dag}
\usepackage[pdftex]{graphicx}
\usepackage{mathrsfs}
\usepackage[colorlinks]{hyperref}

\begin{document}

\bibliographystyle{apsrev}

%
% Title
%

\title{QuantCoin\texttrademark\,-- A quantum computation-backed cryptocurrency}

%
% Authors
%

\author{Peter P. Rohde}
\email[]{dr.rohde@gmail.com}
\homepage{http://www.peterrohde.org}
\affiliation{Centre for Quantum Computation and Intelligent Systems (QCIS), Faculty of Engineering \& Information Technology, University of Technology Sydney, NSW 2007, Australia}

\date{\today}

\frenchspacing

%
% Abstract
%

\begin{abstract}
\end{abstract}

\maketitle

The Bitcoin mining process involves finding bit-strings that hash under SHA256\index{SHA256} to a value within some relatively small range. This so-called `proof-of-work' principle associates computational complexity with the mining process, and since the hashing functions are one-way functions, they must be evaluated via brute-force trial-and-error to find hits.

However, what a waste this is! Our proof-of-work is nothing more than hashing a huge number of random bit-strings, computations which are of no intrinsic value to anyone. The market value in turn has nothing to do with any inherent value earned during the mining process. Rather it is based purely on the psychology of scarcity, since there is an upper bound on the number of Bitcoins that satisfy the legitimacy constraint.

What if we were to replace brute-force hashing of random data with computations of genuine monetary value? Then we would have a sounder currency, whose value derives from the monetary cost of executing useful computations. While it is not so easy to invent such a protocol for classical computation, the idea lends itself very naturally to quantum computation, owing to their ability to undergo encrypted computation and be subject to verification protocols.

Building upon some of the pricing models introduced earlier in this section, there are two main candidates for backing a cryptocurrency with quantum compute-time: the spot market (i.e we execute the computation immediately); and the futures market (i.e we own the right to utilise the computer at some fixed time in the future). We consider the merits of both these candidates.
